A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-08-24 code/figure1v2.Rmd
minor edits

```{r, fig.width = 9, fig.height= 4}
load("../data/cancer_disrupt_heatmap.Rda") ## Load  in data processed in figure1.Rmd

>>>>

---
output:
  word_document: default
  html_document: default
---
```{r, fig.width = 9, fig.height= 4}
load("../data/cancer_disrupt_heatmap.Rda") ## Load  in data processed in figure1.Rmd

### 2020-08-24 text/manuscript.Rmd
minor edits

**Figure 3: Pathway-based classification is independent of tissue-of-origin features.** 
A) Sankey plot showing correspondence between cancer type and cluster identity.
B) Projection of cancer type identity onto UMAP. Abbrevs: BRCA = Breast cancer,
COAD = Colorectal adenocarcinoma, HNSC = Head and neck squamous cell, PAAD =
Pancreatic adenocarcinoma. C) Projection of breast cancer subtypes onto the
UMAP. D) Projection of BRCA1/2 somatic mutation onto the UMAP. E) Projection of
tumor stage onto the UMAP, regardless of cancer type. E) Projection of
metastatic status onto the UMAP. Abbrevs: M0 = non-metastatic tumors, M1 =
metastatic tumors.

>>>>

**Figure 3: Pathway-based clustering independent of tissue-of-origin** 
A) Sankey plot showing correspondence between cancer type and cluster identity.
B) Projection of cancer type identity onto UMAP. Abbrevs: BRCA = Breast cancer,
COAD = Colorectal adenocarcinoma, HNSC = Head and neck squamous cell, PAAD =
Pancreatic adenocarcinoma. C) Projection of breast cancer subtypes onto the
UMAP. D) Projection of BRCA1/2 somatic mutation onto the UMAP. E) Projection of
tumor stage onto the UMAP, regardless of cancer type. E) Projection of
metastatic status onto the UMAP. Abbrevs: M0 = non-metastatic tumors, M1 =
metastatic tumors.
